Fast gravitational wave parameter estimation without compromises

### 2023-07-25 src/tex/ms.tex
Add ROQ, need to check
Finish up ROQ statement

For comparison, we produce equivalent runs with \textsc{Bilby}, using the same
exact data and priors.  We use the \textsc{dynesty} sampler
\citep{2020MNRAS.493.3132S,dynesty}, with 1000 live points and other settings as
in the configurations files available on github \url{https://github.com/kazewong/TurboPE/tree/main/src}.  We
carry out these runs using \textsc{parallel Bilby} (\textsc{pBilby})
\citep{Smith:2019ucc} to distribute the computation over 400 Intel Skylake CPUs
for each event. For the specific settings chosen, the wall-time duration of
each run was ${\sim}2$ h for GW150914 and ${\sim}1$ day for GW170817.
\corr{We have also benchmarked the wall-time performance }

>>>>

For comparison, we produce equivalent runs with \textsc{Bilby}, using the same
exact data and priors.  We use the \textsc{dynesty} sampler
\citep{2020MNRAS.493.3132S,dynesty}, with 1000 live points and other settings as
in the configurations files available on github
\url{https://github.com/kazewong/TurboPE/tree/main/src}.  We carry out these
runs using \textsc{parallel Bilby} (\textsc{pBilby}) \citep{Smith:2019ucc} to
distribute the computation over 400 Intel Skylake CPUs for each event. For the
specific settings chosen, the wall-time duration of each run was ${\sim}2$ h for
GW150914 and ${\sim}1$ day for GW170817. \corr{We have also benchmarked the
performance using a ROQ likelihood, which takes about 30 minutes for GW170817.
Without ROQ, it takes about a week to complete a run. This broadly agrees with
what is suggested in the literature \cite{Smith:2016qas}}
